---
title: 'Electric Company Study: Supplemental Materials'
author: "William Murrah"
date: "2/4/2022"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(texreg)
library(performance)
options(knitr.kable.NA = '')
```


Here we document the decision making process for modeling the Electric Company Study. The code, data. and documentation for this study can be found on the project website at: https://github.com/auqmer/electric_company_Example. 


```{r}
source("code/prepare_WideElectricCompanyData.R")
```


```{r}
source("code/analyze_electricCompany.R")
```

## Analysis of Covariance without and with interaction

To model the impact of exposure to the program, an analysis of covariance was estimated with pre-test as a covariate. This was followed by including an interaction term to see if the relation between pre-test and post-test was different across conditions. 

## Model Comparison

To formally test the two models, we conducted a likelihood ratio test. 
The results are given below.
```{r}
kable(anova(ancova, ancovaX), digits = 2)
```

Below we display both models, noting that the second model was found to be the better fitting model.

```{r, results='asis'}
texreg(list(ancova, ancovaX))
```




